%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Yash Thakur} \\ \vspace{1pt}
    \small  $|$ \href{mailto:yta0088@gmail.com}{\underline{{{email}}}} $|$ 
    \href{https://linkedin.com/in/https://www.linkedin.com/in/sincerelyyyash/}{\underline{linkedin.com/in/{{linkedin}}}} $|$
    \href{https://github.com/https://github.com/sincerelyyyash/}{\underline{github.com/{{github}}}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{undefined}{undefined}{Masters of Computer Applications}{undefined}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Full Stack Engineering Intern}{March 13, 2025 - Present}{CoHatch - KaiLogic LLP}{undefined}
\resumeItemListStart
\resumeItem{Architected and developed a full-stack MVP from scratch, designing scalable system architecture and implementing backend, frontend, and mobile applications for seamless cross-platform functionality.}
\resumeItem{Integrated a core Machine Learning algorithm, optimizing data flow, model deployment, and API interactions to enhance product intelligence.}
\resumeItem{Led end-to-end development, managing backend services, frontend interfaces, API integrations, and cloud deployment to ensure a high-performance, scalable, and production-ready solution.}
\resumeItemListEnd
\resumeSubheading{Software Developer Intern}{April 1, 2023 - August 15, 2025}{Aquaria Solutions}{undefined}
\resumeItemListStart
\resumeItem{Increased application performance by 40% and improved delivery rate by 30% through end-to-end development with Flutter and React, utilizing Agile methodologies.}
\resumeItem{Developed 12 mobile applications with highly responsive UIs, achieving a 4.4/5 average rating and deploying 8 successfully to the Google Play Store and Apple App Store.}
\resumeItem{Collaborated with 5 cross-functional teams, completing 8 major projects ahead of schedule and meeting all deadlines.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Test-AI} $|$ \emph{Next.js, Tailwind CSS, MongoDB, Gemini AI}}{undefined}
\resumeItemListStart
\resumeItem{AI-driven personalized knowledge testing platform.}
\resumeItem{Won the Best UI/UX Award and placed in the Top 10 out of 96 teams at EduHacks 1.0.}
\resumeItem{Developed AI-powered customizable quizzes with real-time assessments and adaptive feedback, increasing user engagement by 25%.}
\resumeItem{Implemented secure authentication and progress tracking using AI algorithms, incorporating image-based questions and a leaderboard system.}
\resumeItemListEnd
\resumeProjectHeading{\textbf{Transsacto} $|$ \emph{Node.js, Express, PostgreSQL, Prisma}}{undefined}
\resumeItemListStart
\resumeItem{Secure banking application backend.}
\resumeItem{Developed APIs for authentication, fund transfers, and transaction management.}
\resumeItem{Integrated Prisma for efficient database operations with PostgreSQL.}
\resumeItem{Collaborated with a teammate on frontend development (Next.js and ShadCN) ensuring seamless integration.}
\resumeItemListEnd
\resumeProjectHeading{\textbf{SneakHeads} $|$ \emph{React, Express, MongoDB, NodeJS, Tailwind, Recoil, Stripe}}{undefined}
\resumeItemListStart
\resumeItem{Full-stack Sneaker E-commerce application.}
\resumeItem{Built a full-stack application supporting 10+ sneaker listings.}
\resumeItem{Designed the landing page with React and managed 15+ API endpoints for efficient data handling.}
\resumeItem{Integrated Stripe for secure payment processing, enhancing user trust and reliability.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages}{: } \\
\textbf{Frameworks}{: React, Next.js, Express} \\
\textbf{Developer Tools}{: } \\
\textbf{Libraries}{: Full-Stack Developer, Node.js, MongoDB, PostgreSQL, Prisma, Tailwind CSS, React-Native, Flutter, API Development, REST, GraphQL, AI, Machine Learning, Agile, Microservices, Scalable Applications, Responsive Dashboards, Real-time Applications, Database Management, Cloud Deployment, Secure Authentication}
    }}
\end{itemize}

\end{document} 